Verifying Demonstrations

### 2017-08-02 primitives.tex
Fixes so that beamerarticle modes are correct
Changes solution section to primitives
Changes section title for primitives
Moves implementation related stuff

\section{Useful Primitives}
\label{UsefulPrimitives}

@@

>>>>

\mode*

\section{Primitives}
\label{Primitives}

@@

From a computational-complexity perspective, operations that must be done on 
the phone must be cheap, other operations may be expensive.

\subsection{Authenticity}

One primitive that fulfils \cref{CreatedAfterStart,CreatedBeforeEnd} is a 
blockchain.
There are also other structures, e.g.\ a directed graph that 
converges~\cite{BlockchainFreeCryptocurrencies}.
For generality, we will use the terminology of 
\textcite{BlockchainFreeCryptocurrencies} and simply call this storage 
structure \iac{tposet}.

\begin{frame}
  \begin{question}
    What about distributed voting/polling protocols?
    A tree should give a strict partial order?
  \end{question}
  \begin{question}
    Can linear blockchains also fit in the framework of 
    \textcite{BlockchainFreeCryptocurrencies}?
    Can we generalize it?
  \end{question}
\end{frame}

\Cref{CreatedBeforeEnd} is straight-forward, Alice and Bob simply add their 
proofs to the \ac{tposet} \emph{in (time-wise) relation to the event}.
Then we know that they cannot have been created after the event.

\begin{frame}<presentation>
  \begin{solution}[A\ref{CreatedBeforeEnd} Created before end]
    \begin{itemize}
      \item Make the \ac{LP} part of the \ac{tposet}.
      \item The proof must've been created before it was included (duh!).
      \item (Also related to V\ref{EligibilityVerif}.)
    \end{itemize}
  \end{solution}
\end{frame}

For \cref{CreatedAfterStart} Alice and Bob must include an unpredictable value 
in their proofs, e.g.\ the \enquote{head} of the \ac{tposet}.
This means that they cannot create a proof and keep it for a future protest.

They can use an older value (pick one from the history of the \ac{tposet}) when 
they create their proofs.
This will only expand the interval of possible creation into the past.
This will not help their cause, as anyone will recognize that the proof could 
be created at any time in that interval.

\begin{frame}
  \mode<presentation>{
  \begin{idea}[A\ref{CreatedAfterStart} Created after start]
    \begin{itemize}
      \item Include an unpredictable value in the \ac{LP}.
      \item This could be e.g.\ the hash of the \enquote{head} of the 
        \ac{tposet}.
      \item This prevents creating proofs for future protests.
    \end{itemize}
  \end{idea}
  }

  \pause

  \begin{question}
    How hard is it to reuse old proofs?
    Forge all signatures due to changed values?
  \end{question}
\end{frame}

\subsection{Location proofs}

If we include \iac{LP}, this will tie the proof to the physical location and, 
thus, solve \cref{SpatiallyRelated}.
The \ac{LP} is \enquote{witnessed} (signed) by other participants.
The \ac{LP} contains coarse coordinates of the location, which must be within 
the protest area to be valid.
This allows Bob the protester to move within the protest area to collect 
witnesses (signatures).
It also provides privacy since the location cannot be used to deanonymize Bob's 
proof --- e.g.\ to correlate the location in his proof with captured 
surveillance footage.

\begin{frame}
  \mode<presentation>{
  \begin{idea}[A\ref{SpatiallyRelated} Correct location]
    \begin{itemize}
      \item The \ac{LP} is \enquote{witnessed} (signed) by other participants.
      \item We have a coarse location, just within protest area.
      \item This allows protesters to move around to collect signatures.
      \item This provides privacy for the location, e.g.\ cannot map to 
        surveillance cameras.
    \end{itemize}
  \end{idea}
  }

  \pause

  \begin{question}
    How can we do \acp{LP} with 1000s of witnesses each?
    Can we do some preprocessing?
    Ad-hoc networks, broadcast \acp{LP}?
  \end{question}
  \begin{question}
    Why should anyone trust these witnesses?
    What are the assumptions?
    Signed over a short period of time?\footnote{%
      In a sense, if they collude they have shown support for the cause.
      As long as they are not Sybil it should be fine?
    }
  \end{question}
  \begin{question}
    Trusted party for the group signatures?
  \end{question}
  \begin{question}
    Must tie credentials to something unique: phone, phone subscription?
    Cannot register twice, government control?
  \end{question}
\end{frame}

\subsection{Storage}

\begin{frame}
  \begin{question}
    Malicious nodes want to provide Alice with a view that her proof is 
    included.
    Everyone else is provided a view without Alice.
    How can we ensure a consistent view for everyone?
    (Probably similar to the solution in Joakim's thesis.)
  \end{question}

  \begin{question}
    Under the protest conditions, we might have natural network splits.
    Is this a useful scenario?
  \end{question}

  \begin{question}
    How can we do blockchain branch and merge?
    That is needed to recover from the above attack.
  \end{question}
\end{frame}

\begin{frame}
  \begin{question}
    What can we achieve with a consensus protocol?
    Majority must be honest?
  \end{question}
  \begin{question}
    What is a suitable proof-of-work?
    See e.g.~\cite{FairProofOfWork}.
  \end{question}
\end{frame}

\subsection{Verifiability}

\begin{frame}
  \begin{question}
    How to solve the Sybil problem?
    Can we piggyback on existing \acp{PKI}?
    E.g.~\cite{Cinderella}.
  \end{question}
  \begin{question}
    This is similar to the double-spending problem for cryptocurrencies, can 
    we reuse any such techniques?
    Specifically ecash~\cite{ecash} and the like.
  \end{question}
\end{frame}

### 2017-08-02 properties.tex
Moves implementation related stuff

    \item A\ref{SpatiallyRelated} is provided by \iacf{LP}.
  \end{itemize}
\end{idea}
}
\end{frame}
\Cref{CreatedBeforeEnd,CreatedAfterStart} requires a \emph{partial 
  order}\footnote{%
  A relation \(\preceq\) which is reflexive, antisymmetric and transitive.
}.
If some objects in the set relate to known points in time, then the partial 
order allows to relate the data to the time of the event.
This allows us to \emph{authenticate the data temporally}.
\Cref{SpatiallyRelated} binds the data spatially to the location, which allows 
us to \emph{authenticate the data spatially}.

One primitive that fulfils \cref{CreatedAfterStart,CreatedBeforeEnd} is a block 
chain.

\begin{frame}
  \begin{question}
    Are there other structures than block chains?
    E.g.~\cite{BlockchainFreeCryptocurrencies}.
  \end{question}
  \begin{question}
    What about distributed voting/polling protocols?
    A tree should give a strict partial order?
  \end{question}
\end{frame}

\Cref{CreatedBeforeEnd} is straight-forward, we simply add the proof to the 
block chain \emph{in (time-wise) relation to the event}.
Then we know that it cannot have been created after the event.

\begin{frame}<presentation>
  \begin{solution}[A\ref{CreatedBeforeEnd} Created before end]
    \begin{itemize}
      \item Make the \ac{LP} part of the block chain.
      \item The proof must've been created before it was included (duh!).
      \item (Also related to V\ref{EligibilityVerif}.)
    \end{itemize}
  \end{solution}
\end{frame}

For \cref{CreatedAfterStart} we must include an unpredictable value in the 
proof, e.g.\ the head of the block chain.
This means that we cannot create a proof and keep it for a future protest.
This also prevents us from reusing proofs from previous protests.

\begin{frame}
  \mode<presentation>{
  \begin{idea}[A\ref{CreatedAfterStart} Created after start]
    \begin{itemize}
      \item Include an unpredictable value in the \ac{LP}.
      \item This could be e.g.\ the hash of the head of the block chain.
      \item This prevents creating proofs for future protests.
    \end{itemize}
  \end{idea}
  }

  \begin{question}
    How will this prevent us from reusing proofs from previous protests in 
    the same location(s)?
    What are the assumptions?
  \end{question}
  \begin{question}
    How hard is it to reuse old proofs?
    Forge all signatures due to changed values?
  \end{question}
\end{frame}

If we include \iac{LP}, this will tie the proof to the physical location and, 
thus, solve \cref{SpatiallyRelated}.
The \ac{LP} is \enquote{witnessed} (signed) by other participants.
The \ac{LP} contains coarse coordinates of the location, which must be within 
the protest area to be valid.
This allows Bob the protester to move within the protest area to collect 
witnesses (signatures).
It also provides privacy since the location cannot be used to deanonymize Bob's 
proof --- e.g.\ to correlate the location in his proof with captured 
surveillance footage.

\begin{frame}
  \mode<presentation>{
  \begin{idea}[A\ref{SpatiallyRelated} Correct location]
    \begin{itemize}
      \item The \ac{LP} is \enquote{witnessed} (signed) by other participants.
      \item We have a coarse location, just within protest area.
      \item This allows protesters to move around to collect signatures.
      \item This provides privacy for the location, e.g.\ cannot map to 
        surveillance cameras.
    \end{itemize}
  \end{idea}
  }

  \begin{question}
    How can we do \acp{LP} with 1000s of witnesses each?
    Can we do some preprocessing?
    Ad-hoc networks, broadcast \acp{LP}?
  \end{question}
  \begin{question}
    Why should anyone trust these witnesses?
    What are the assumptions?
    Signed over a short period of time?\footnote{%
      In a sense, if they collude they have shown support for the cause.
      As long as they are not Sybil it should be fine?
    }
  \end{question}
  \begin{question}
    Trusted party for the group signatures?
  \end{question}
  \begin{question}
    Must tie credentials to something unique: phone, phone subscription?
    Cannot register twice, government control?
  \end{question}
\end{frame}

@@

In general, protesting is very similar to voting: both are many individuals 
expressing their opinion.
Hence we desire to have similar properties of verification and privacy for 
participation in a protest as there is for voting.
In the context of (electronic) voting protocols, there are three requirements 
for verification~\cite{VerifyingPrivacyPropertiesOfVotingProtocols}:
\begin{frame}
\begin{requirements}[V]
\item\label{EligibilityVerif} Eligibility: anyone can verify that each vote 
  cast is legitimate.
\item\label{UniversalVerif} Universal verifiability: anyone can verify that the 
  result is according to the cast votes.
\item\label{IndividualVerif} Individual verifiability: every voter can verify 
  that their vote is included in the result.
\end{requirements}
\end{frame}
We can translate these to the case of participation in a demonstration, then 
each vote would be replaced by a proof of participation.
To have any verifiability, we need the storage (i.e.\ block chain) to be 
immutable.
So we need a consensus protocol which prevents malicious changes.

\begin{frame}
  \mode<presentation>{
  \begin{remark}
    \begin{itemize}
      \item For valid verification we must have an immutable block chain.
      \item We need something like a consensus protocol to prevent malicious 
        changes.
    \end{itemize}
  \end{remark}
  }

  \begin{question}
    What can we achieve with a consensus protocol?
    Majority must be honest?
  \end{question}
  \begin{question}
    What is a suitable proof-of-work?
    See e.g.~\cite{FairProofOfWork}.
  \end{question}
\end{frame}

If the proofs are included in a public block chain (as suggested in 
\cref{DataAuthenticity}), then an individual can check that their proof has 
been included in the chain.
Thus \cref{IndividualVerif} is fulfilled.

\begin{frame}
  \mode<presentation>{
  \begin{idea}[V\ref{IndividualVerif} Individual verifiability]
    \begin{itemize}
      \item Proofs are stored publicly (block chain).
      \item Each participant can check that their proof is indeed included.
    \end{itemize}
  \end{idea}
  }

  \begin{question}
    Malicious nodes want to provide Alice with a view that her proof is 
    included.
    Everyone else is provided a view without Alice.
    How can we ensure a consistent view for everyone?
    (Probably similar to the solution in Joakim's thesis.)
  \end{question}
\end{frame}

@@

\begin{frame}
  \mode<presentation>{
  \begin{idea}[V\ref{EligibilityVerif} Eligibility]
    \begin{itemize}
      \item Must verify that the proof is not reused from before 
        (A\ref{CreatedAfterStart} and A\ref{CreatedBeforeEnd}).
      \item Must verify that each proof belongs to a unique individual (not 
        only Sybil).
    \end{itemize}
  \end{idea}
  }

  \begin{question}
    How to solve the Sybil problem?
    Can we piggyback on existing \acp{PKI}?
    E.g.~\cite{Cinderella}.
  \end{question}
  \begin{question}
    This is similar to the double-spending problem for cryptocurrencies, can 
    we reuse any such techniques?
  \end{question}
\end{frame}

If the block chain is public, then anyone can download all the proofs, verify 
them (eligibility) and count them.
Thus anyone can verify the result, which fulfils \cref{UniversalVerif}.

\begin{frame}
  \mode<presentation>{
  \begin{idea}[V\ref{UniversalVerif} Universal verifiability]
    \begin{itemize}
      \item Proofs are stored publicly.
      \item Anyone can download all proofs, verify them and then count them.
    \end{itemize}
  \end{idea}
  }

  \begin{question}
    Similar as before: how can we ensure consistent views for everyone?
  \end{question}
\end{frame}

@@

A demonstration is very different from voting in one sense: Alice must be 
physically present and that very presence shows her support for the cause.
In voting, on the other hand, Alice has multiple options which are not revealed
by her mere presence.
% XXX Check if unlinkable is the correct term
Hence, if Alice submits a proof to the block chain, the proof must be 
unlinkable to Alice, yet, if Alice submits another proof, those two proofs must 
be linkable (due to eligibility verification, \cref{EligibilityVerif}).
E.g.\ Eve compromises Alice's device (and private keys).
Anyone can verify any proof.
With the inputs that Eve can extract from the published proof and the keys she 
can find on Alice's device, she should not be able to reproduce the same 
signatures on the proof.
So Alice needs a long-term and a short-term credential, but she should not be 
able to create two short-term credentials to participate twice.

>>>>

    \item A\ref{SpatiallyRelated} can be provided by \iacf{LP}.
  \end{itemize}
\end{idea}
}
\end{frame}
\Cref{CreatedBeforeEnd,CreatedAfterStart} requires a \emph{partial 
  order}\footnote{%
  A relation \(\preceq\) which is reflexive, antisymmetric and transitive.
}.
If some objects in the set relate to known points in time, then the partial 
order allows to relate the data to the time of the event.
This allows us to \emph{authenticate the data temporally}.
\Cref{SpatiallyRelated} binds the data spatially to the location, which allows 
us to \emph{authenticate the data spatially}.

@@

In general, protesting is very similar to voting: both are many individuals 
expressing their opinion.
Hence we desire to have similar properties of verification and privacy for 
participation in a protest as there is for voting.
In the context of (electronic) voting protocols, there are three requirements 
for verification~\cite{VerifyingPrivacyPropertiesOfVotingProtocols}:
\begin{frame}
\begin{requirements}[V]
\item\label{EligibilityVerif} Eligibility: anyone can verify that each vote 
  cast is legitimate.
\item\label{UniversalVerif} Universal verifiability: anyone can verify that the 
  result is according to the cast votes.
\item\label{IndividualVerif} Individual verifiability: every voter can verify 
  that their vote is included in the result.
\end{requirements}
\end{frame}
We can translate these to the case of participation in a demonstration, then 
each vote would be replaced by a proof of participation.
To have any verifiability, we need the storage (e.g.\ blockchain) to be 
immutable --- i.e.\ it prevents malicious changes.

\begin{frame}<presentation>
  \begin{remark}
    \begin{itemize}
      \item For valid verification we must have immutable storage.
      \item We need to prevent or detect malicious changes.
    \end{itemize}
  \end{remark}
\end{frame}

If the proofs are stored publicly, then an individual can check that their 
proof has been included there.
Thus \cref{IndividualVerif} is fulfilled.

\begin{frame}<presentation>
  \begin{idea}[V\ref{IndividualVerif} Individual verifiability]
    \begin{itemize}
      \item Proofs are stored publicly (e.g.\ blockchain).
      \item Each participant can check that their proof is indeed included.
    \end{itemize}
  \end{idea}
\end{frame}

@@

\begin{frame}<presentation>
  \begin{idea}[V\ref{EligibilityVerif} Eligibility]
    \begin{itemize}
      \item Must verify that the proof is not reused from before 
        (A\ref{CreatedAfterStart} and A\ref{CreatedBeforeEnd}).
      \item Must verify that each proof belongs to a unique individual (not 
        only Sybil).
    \end{itemize}
  \end{idea}
\end{frame}

If the blockchain is public, then anyone can download all the proofs, verify 
them (eligibility) and count them.
Thus anyone can verify the result, which fulfils \cref{UniversalVerif}.

\begin{frame}<presentation>
  \begin{idea}[V\ref{UniversalVerif} Universal verifiability]
    \begin{itemize}
      \item Proofs are stored publicly.
      \item Anyone can download all proofs, verify them and then count them.
    \end{itemize}
  \end{idea}
\end{frame}

@@

A demonstration is very different from voting in one sense: Alice must be 
physically present and that very presence shows her support for the cause.
In voting, on the other hand, Alice has multiple options which are not revealed
by her mere presence.
% XXX Check if unlinkable is the correct term
Hence, if Alice submits a proof to the blockchain, the proof must be 
unlinkable to Alice, yet, if Alice submits another proof, those two proofs must 
be linkable (due to eligibility verification, \cref{EligibilityVerif}).
E.g.\ Eve compromises Alice's device (and private keys).
Anyone can verify any proof.
With the inputs that Eve can extract from the published proof and the keys she 
can find on Alice's device, she should not be able to reproduce the same 
signatures on the proof.
So Alice needs a long-term and a short-term credential, but she should not be 
able to create two short-term credentials to participate twice.
